%!TEX root=../main.tex


\section {An Open Monitoring Ecosystem}

To address the disadvantages of the locked down nature of the existing infrastructures, we propose as a solution an ecosystem consisting of a federation of applications that support a learner in accelerating vocabulary acquisition. The ecosystem is built on the following principles:

\begin{description}

	\item [Free Reading.] The learners are able to read the materials they find interesting with the applications they prefer to read with. When a learner encounters a word he does not understand, a high-quality, contextual translation should be offered.

	\item [Ubiquitous Monitoring.] All the encounters of a learner with foreign materials are monitored in order to build an evolving model of the current state of the knowledge of the learner. The applications that are part of the ecosystem report a users interactions with the texts to a central repository.

	\item [Accelerated Learning.] Based on the learner model intelligent agents recommend materials that are both likely to be interesting to the reader and at the same time maximize the likelihood of retaining the most important learned words at the optimal times. Also, since the context of the looked up word is saved with the word, the context can be used to accelerate retention.

	\item [Openness.] The ecosystem is open to any reader or trainer application, be it academic or for profit, as long as it contributes back to the ecosystem. The data about a given leaner belongs to them and it is them who decide which applications have access their data.

\end{description}

Note that although we present an ecosystem which is targeted at learning a vocabulary, {\bf ubiquitous monitoring ecosystems} can be used for other types of assistance as long as they represent {\em federations of applications that jointly monitor a certain aspect of a users interaction with data and contribute to a centralized model of the user which is then used to serve the user better in achieving their goals}.

It might appear intuitive for the reader that such an ecosystem will present a network effect: the more contexts in which the reader is supported by applications from the ecosystem, the better the knowledge model of that learner that can be built, and the better the provided user experience.


% Move to discussion! 
% The reasons for the various participants in this ecosystem are different, but everybody has something to gain: 

% \begin{itemize}
% 	\item The Reader Applications. They receive information about the preferences of the user as well as his current knowledge of the various topics. They do not have to worry about storing the information about 

% 	\item The Trainer Applications. They receive information about the current knowledge of the user, and can better tailor exercises for them.
	
% 	\item The user. By using applications in the monitoring ecosystem, he has the confidence that his knowledge is mo

% 	\item The Core of the System. Can benefit from running anonymized analyses and discover trends and run scientific experiments.
% \end{itemize}

